---
title: "Basic flexdashboard with Shiny components"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
# Make sure you include runtime: shiny in your R Markdown header (up top) to enable Shiny functionality
library(flexdashboard)
library(tidyverse)
library(gapminder)
```

Overview
========================================

Column {data-width=200 .sidebar}
-----------------------------------------------------------------------

```{r}
# Input for user to filter by continent
selectInput(inputId = "continent", label = "Continent", choices = levels(gapminder$continent))

# Input for user to filter by year
sliderInput(inputId = "year", label = "Year", min = 1952, max = 2007, step = 5, value = c(1952, 2007))

# Make the data reactive to the user input
gapminder_reactive <- reactive({
  
  gapminder %>%
    # input$inputId, input$year[1] represents the lower year, input$year[2] represents the upper year 
    filter(continent == input$continent, year >= input$year[1], year <= input$year[2])

  }) 
```

Column {data-width=400}
-----------------------------------------------------------------------

### Scatter plot

```{r}
# Shiny interactive scatter plot
renderPlot({gapminder_reactive() %>%
    ggplot(aes(x = gdpPercap, y = lifeExp)) +
    geom_point()
})
```

### Histogram

```{r}
# Load plotly to use renderPlotly() for interactive plot
library(plotly)

# Shiny interactive histogram
renderPlotly({gapminder_reactive() %>%
  ggplot(aes(x = lifeExp)) +
  geom_histogram(bins = 30)
})
```


Column {data-width=400}
-----------------------------------------------------------------------

### Median Life Expectancy

```{r}
renderValueBox({
  median_lifeExp <- gapminder_reactive() %>% 
  summarise(median_lifeExp = round(median(lifeExp), 0)) %>%
  pull()
  
  valueBox(median_lifeExp,
    caption = "Median Life Expectancy",
    icon = "fa-heartbeat")
})
# More icons for your value box here: https://fontawesome.com/icons?d=gallery&q=health
```

### Fitted Values `lifeExp ~ country + continent + year + gdpPercap` {data-height=360}

```{r}
# Fit multiple linear regression model
fit <- lm(lifeExp ~ country + continent + year + gdpPercap, data = gapminder)

# Table of fitted values, residuals and other stats 
library(broom)
fitted_residuals <- augment(fit)

# Clean table
fitted_residuals_clean <- fitted_residuals %>%
  select(-.se.fit, -.hat, -.sigma, -.cooksd, -.std.resid) %>%
  rename(Fitted = .fitted, Residual = .resid) 
  
# Make the table reactive to the user input
fitted_residuals_clean_reactive <- reactive({
  
  fitted_residuals_clean %>%
    # input$inputId, input$year[1] represents the lower year, input$year[2] represents the upper year 
    filter(continent == input$continent, year >= input$year[1], year <= input$year[2])

  })

# Reactive table of fitted values, residuals and other stats 
renderTable({
  fitted_residuals_clean_reactive() %>%
    select(country, year, gdpPercap, lifeExp, Fitted)
  })
```

### Fitted vs. Actual {data-height=600}

```{r}
renderPlot({
  fitted_residuals_clean_reactive() %>%
    gather(fitted_actual, value, lifeExp, Fitted) %>%
    ggplot(aes(x = year, y = value, colour = fitted_actual, group = fitted_actual)) +
    geom_point() +
    geom_line() +
    labs(y = "Life expectancy", x = "Year") +
    theme(axis.text.x = element_text(size = 10, angle = 45)) +
    scale_y_continuous(limits = c(0, 100), breaks = seq(40, 80, 20), expand = c(0, 0)) +
    facet_wrap(~ country) 
  })
```

Modelling
========================================

Column {data-width=500}
-----------------------------------------------------------------------

### Model explanation

Model of life expectancy using the following independent variables:

* `country`
* `continent`
* `year`
* `gdpPercap`

The model explains 93% of the variation in life expectancy.

```{r eval=FALSE}
#glance(fit)
```

Estimated coefficients, standard errors, t-statistics and p-values from the fitted model shown below:

```{r}
library(DT)
tidy(fit) %>% datatable()
```

Column {data-width=500}
-----------------------------------------------------------------------

### Predictions

**Limitation: Continent and country inputs should be conditional on each other. Select a valid combination.**

```{r}
# Inputs for prediction
selectInput(inputId = "continent_pred", label = "Continent", choices = levels(gapminder$continent))
selectInput(inputId = "country_pred", label = "Country", choices = levels(gapminder$country))
numericInput(inputId = "year_pred", label = "Year", value = 2007, min = 1952, max = 2007)
numericInput(inputId = "gdpPercap_pred", label = "GDP Per Capita", value = 10000, min = 0, max = 120000)

# Inputs as reactive table
user_input_data <- reactive({
  
    tibble(continent = input$continent_pred,
           country = input$country_pred, 
           year = input$year_pred, 
           gdpPercap = input$gdpPercap_pred)

  })

# Prediction: table
renderTable({
  augment(fit, newdata = user_input_data()) %>%
    rename(Prediction = .fitted)
  })
```