---
title: "How to create animation with gganimate in R"
author: "Jiaying Wu"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 6,
                      fig.height = 4,
                      fig.align = "center",
                      gganimate = list(
                        width = 600, 
                        height = 400
                      ))
```

This note provide a introduction to create animation in R using the `gganimate` package.

### What is `gganimate`?

`gganimate` is an extension of the `ggplot2` package for creating animated ggplots. It provide a range of new functionality that can be added to the plot object in order to customize how it should change with time.

3 main class of functions in `gganimate`:

- `transition_*()` defines how the animation should run over time. 

- `view_*()` defines how the axis scales should change over time.

- `shadow_*()` defines how data from previous time should be presented in the current time.

### Prerequisites

```{r library}
# data wrangling
library(dplyr)
# static plot
library(ggplot2)
# animation
library(gganimate)
# data set
library(gapminder)
```

### Data set

```{r data}
gapminder
```

### Step 1: Create a static plot

```{r static}
stat_scatter <- ggplot(data = gapminder, aes(x = gdpPercap, y=lifeExp, size = pop, colour = country)) +
  geom_point(show.legend = FALSE, alpha = 0.7) +
  # scale the color
  scale_color_viridis_d() +
  # scale the point size
  scale_size(range = c(2, 12)) +
  scale_x_log10() +
  labs(x = "GDP per capita", y = "Life expectancy")
stat_scatter
```

### Step 2: Define how the animation should run with `transition_*()`

Transition function: `transition_time()` splits the data into subsets based on a variable in the data, the animation go through each subset over time.

Label variables: `frame_time`. Gives the time that the current frame corresponds to.

```{r transition}
stat_scatter +
  # transition function
  transition_time(year) +
  # label variable
  labs(title = "Year: {frame_time}")
```

```{r state}
filter(gapminder, year == 1952)
```

8 ore transition functions:

- `transition_time()`

- `transition_reveal()`

- `transition_null()`

- `transition_filter()`

- `transition_layers()`

- `transition_manual()`

- `transition_components()`

- `transition_events()`

Use the `?` view the R Documentation.

### Step 3: Define how the axis scale should change with `view_*()`

`view_follow`: set the axis scale follow the in each frame.

```{r view}
stat_scatter +
  # transition function
  transition_time(year) +
  # label variable
  labs(title = "Year: {frame_time}") +
  # view function
  view_follow(fixed_y = TRUE)
```

5 more view functions:

- `view_static()`

- `view_zoom()`

- `view_step_manual()`

- `view_step()`

- `view_step_manual()`

Use the `?` view the R Documentation.


### Step 4: Define how data from previous time should be presented in the current time with `shadow_*()`

`shadow_wake()` draw a small wake after data by showing the latest frames up to the current.

```{r shadow}
stat_scatter +
  # transition function
  transition_time(year) +
  # label variable
  labs(title = "Year: {frame_time}") +
  # view function
  view_follow(fixed_y = TRUE) +
  # shadow function
  shadow_wake(wake_length = 0.1, alpha = FALSE)
```

3 more shadow functions:

- `shadow_null()`

- `shadow_mark()`

- `shadow_trail()`

Use the `?` view the R Documentation.


### Step 5: Control how the animate being render with `animate()`

- `nframes` sets the number of frames (defaults to `100`)

-`fps` sets the frames per second (defaults to `10`)

- `dev` sets the device used to render each frame (defaults to 'png')

- renderer sets the function used to combine each frame into an animate (defaults to gifski_renderer())

```{r animate}
anim <- stat_scatter +
  # transition function
  transition_time(year) +
  # label variable
  labs(title = "Year: {frame_time}") +
  # view function
  view_follow(fixed_y = TRUE) +
  # shadow function
  shadow_wake(wake_length = 0.1, alpha = FALSE)

animate(plot = anim, 
        nframes = 80, 
        fps = 5, 
        renderer = gifski_renderer(loop = FALSE))
```

### Step 6: Save the animation in your local computer

```{r save_animate}
anim_save(filename = "anim_lifeExp_gdp.gif", 
          animation = anim,
          nframes = 80, 
          fps = 8)
```


### Reference

- Kassambara. 2020. gganimate: How to Create Plots with Beautiful Animation in R. Retrieved from https://www.datanovia.com/en/blog/gganimate-how-to-create-plots-with-beautiful-animation-in-r/

- Thomas, L.2020. gganimate. Retrieved from https://github.com/thomasp85/gganimate
