---
title: "Course 1 Section 2.24 - Pedestrian activity around the City of Melbourne 2"
author: "Jiaying Wu"
date: "15/09/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE)
```

```{r library}
library(tidyverse)
library(here)
```

### Step 1: Create a new R Markdown and read in the data

```{r ped}
ped <- read_csv(here("data", "melb_walk.csv"))
ped
```

### Step 2: Count the sensors, and more

#### Q1: Use a wrangling verb, to count the number of sensors. Do all the sensors have the same number of measurements?

```{r S2Q1}
num_sensor <- ped %>%
  group_by(Sensor) %>%
  summarise(num_sensor = n())

num_sensor
```

```{r check_sensor}
unique(num_sensor$num_sensor)
```

All the sensors have the same number of measurements.

#### Q2: For each sensor, compute the total count for January. Which sensor had the largest count? Which sensor had the smallest count?

```{r count_by_sensor}
count_by_sensor <- ped %>%
  group_by(Sensor) %>%
  summarise(sum = sum(Count, na.rm = TRUE)) %>%
  arrange(sum)
```

```{r smallest}
head(count_by_sensor)
```

```{r largest}
tail(count_by_sensor)
```

### Q3: For each sensor, compute the total number of missing counts. Which sensor had the most missing counts? Why might this be?

```{r missing_count}
ped %>%
  group_by(Sensor) %>%
  select(Count) %>%
  summarise_all(funs(sum(is.na(.)))) %>%
  rename(na_count = "Count") %>%
  arrange(desc(na_count))
```

#### Q4: Create a new table that contains the counts for the Melbourne Central and State Library sensors, then use a tidying verb to create two new columns that contain their counts.

```{r two_station}
ped %>%
  filter(Sensor %in% c("Melbourne Central", "State Library")) %>%
  spread(key = Sensor, value = Count)
```

#### Q5: Create the following 100 percent chart to compare the foot traffic at Melbourne Central and the State Library during different hours of the day. Explain why the first 8 days of January appear this way.

```{r 100_bar, fig.height = 6, fig.width= 10}
ped %>%
  filter(Sensor %in% c("Melbourne Central", "State Library")) %>%
  ggplot(aes(x = Time , y = Count, fill = Sensor)) +
  geom_bar(stat = "identity", position = "fill") +
  facet_wrap(~Date, ncol = 7)
```



