---
title: "Course 1 Section 2.14 - Tidy data"
author: "Jiaying Wu"
date: "14/09/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE)
```

```{r library}
library(tidyverse)
```

```{r load_data}
kb <- read_csv("https://raw.githubusercontent.com/datascienceprogram/ids_course_data/master/koala_bilby.csv")
kb
```

### Exercise 1

Once you’ve read the data into your R session, gather the data into long form, naming the two new variables, label and count.

```{r kb_long}
kb_long <- gather(kb, key = "label", value = "count", -ID)
kb_long
```

### Exercise 2

Separate the labels into two new variables: animal and state.

```{r kb_separate}
kb_separate <- separate(kb_long, 
                        col = label, 
                        into = c("animal", "state"),
                        sep = "_")
kb_separate
```

### Exercise 3

Spread the long form data into wide form, where the columns are the states.

```{r kb_wide}
kb_wide <- spread(kb_separate, key = "state", value = "count")
kb_wide
```

### Exercise 4

Spread the long form data into wide form, where the columns are the animals.

```{r kb_animal}
kb_animal <- spread(kb_separate, key = "animal", value = "count")
kb_animal
```


