---
title: "Course 2 Section 1.11 - Your turn"
author: "Jiaying Wu"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      fig.width = 8,
                      fig.height = 4,
                      fig.align = "center")
```

### Step 1: Reading the data

```{r read_agencies}
# Load tidyverse
library(tidyverse)

# URL of raw text from GitHub
agencies_URL <- "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-01-15/agencies.csv"

# Read agencies data
agencies <- read_csv(agencies_URL)
```

```{r read_launches}
# URL of raw text from GitHub
launches_URL <- "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-01-15/launches.csv"

# Read agencies data
launches <- read_csv(launches_URL)
```


### Step 2: Examine each data set

```{r agencies}
# Look at agencies
glimpse(agencies)
```

```{r launches}
# Look at launches
glimpse(launches)
```

#### Q1: How many distinct agencies (space launch providers) are in the data set agencies?

```{r agencies_distinct}
# 1. Check if each row in agencies is distinct (should return same data)
agencies %>%
  distinct()
```


#### Q2: Which variable in agencies uniquely describes each agency?

```{r agencies_unique}
# 2. Variable that uniquely describes each space launch providers 
agencies %>%
  distinct(agency)
```

"agency" varaible return the same number of row, it mean the "agency" varaible uniquely describes each agency.

#### Q3: Is there an agency that has more than one organisation phase code? If so, which agency?

```{r}
# 3. Compare with above to see if there is an agency with more than one org phase code
agencies %>%
  distinct(ucode)
```

Variable "agency" is the org phase code。

#### Q4: Why might an agency have more than one organisation phase code?

```{r}
# 4. Number of distinct agency code for each agency name
agencies %>%
  group_by(name) %>%
  summarise(num_agency_code = n_distinct(agency)) %>%
  ungroup() %>%
  arrange(desc(num_agency_code))
```

```{r}
# Filter for Sea Launch Limited Partnership
agencies %>%
  filter(name == "Sea Launch Limited Partnership")
```

### Step 3: Joining tables together

obtain the number of agencies that provided a space launch.

#### Join agencies to launches

```{r}
# Left join agencies to launches
launches_agencies <- left_join(launches, agencies, by = "agency")

# Print launches_agencies
launches_agencies
```

#### Retain matching phase codes

```{r}
# Join to retain only observations with matches
launches_agencies <- inner_join(launches, agencies, by = "agency")

# Print launches_agencies
launches_agencies
```

### Step 4: Data visualisation on joined tables

```{r}
# Overlapping bar plot of successful and failed launches for each space agency
launches_agencies %>%
  ggplot(aes(x = name, fill = category)) +
  geom_bar(position = position_dodge(width = 0.2), alpha = 0.5) + # adjust bar position & reduce colour transparency
  labs(title = "Launch Outcomes", x = "Space Agency", y = "Frequency") +
  scale_fill_discrete(name = "Outcome", labels = c("Failure", "Success")) + # change legend title and labels
  theme(legend.position = "bottom") +
  coord_flip() # flips the x and y coordinates
```

Note that we can certainly improve the visualisation of total failed and successful space launches by agency with some data wrangling.

```{r}
# Wrangling: Create tidy data frame of count of successful and failed launches
success_fail_count <- launches_agencies %>%
  group_by(short_name, category) %>%
  summarise(n_success_fail = n()) %>%
  ungroup() %>%
  spread(category, n_success_fail) %>%
  rename(Success = O, Fail = `F`) %>%
  mutate(Success = replace_na(Success, 0),
         Fail = replace_na(Fail, 0),
         Total_Launch = Fail + Success) %>%
  # Order space agency by total launches
  mutate(short_name = fct_reorder(short_name, Total_Launch)) %>%
  gather(Outcome, Count, -short_name)

# Plotting: Overlapping bar plot of successful and failed launches for each space agency
success_fail_count %>%
  filter(Outcome != "Total_Launch") %>%
  ggplot(aes(x = short_name, y = Count, fill = Outcome)) +
  geom_bar(stat = "identity") + 
  labs(title = "Launch Outcomes", x = "Space Agency", y = "Frequency") +
  # colours based on Dark2 colour palette
  scale_fill_manual(values = c("#D95F02", "#1B9E77")) +
  facet_wrap(~ Outcome, scales = "free_x") +
  coord_flip()
```

Which launch vehicles are in the top five highest number of launches and which space agency do they come from?

```{r}
# Plot of launch vehicle by frequency
launches_agencies %>%
  group_by(short_name, state_code.y, type.x) %>%
  summarise(freq_launchvehicle = n()) %>%
  # Return vehicle with highest launch number
  top_n(1, freq_launchvehicle) %>%
  ungroup() %>%
  ggplot(aes(x = fct_reorder(short_name, freq_launchvehicle), y = freq_launchvehicle, colour = state_code.y)) +
  geom_text(aes(label = type.x), size = 3) +
  labs(title = "Number of times vehicle was launched", x = "Space Agency", y = "Frequency") +
  scale_colour_discrete(name = "State Responsible", labels = c("Cayman Island", "France", "Japan", "Russia", "USA")) +
  coord_flip()
```



