---
title: "Course 2 Section 1.17 - Your turn"
author: "Jiaying Wu"
date: "04/10/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      fig.width = 5,
                      fig.height = 4,
                      fig.align = "center")
```

```{r library}
library(tidyverse)
library(naniar)
library(visdat)
```

```{r data}
# Read the data
houses <- read_csv(here::here("data", "Melbourne_housing_FULL.csv"))
```

### Examine house prices in Melbourne, Australia

#### Q1. Make an overview plot of the full data. Which variables have missings? Focus only on the variables Price, Rooms, Type, Distance, Bedroom2, Bathroom.

```{r miss_color}
# 1. Keep only variables Price, Rooms, Type, Distance, Bedroom2, Bathroom
houses_sub <- houses %>% 
  select(Price, Rooms, Type, Distance, Bedroom2, Bathroom)

# Map of data coloured by variable type and NA
houses_sub %>%
  vis_dat()
```

```{r miss_map}
# Missingness map 
houses_sub %>%
  vis_miss()
```

#### Q2. Make a missing values summary of all the data. What proportion of observations are missing on Price?

```{r miss_var}
# 2. Missing variables summary table
miss_var_summary(houses_sub)
```

#### Q3. Remove the observations that have missing values on Price because this is the response variable that we want to ultimately predict. You can’t build a stable model of house price if you don’t know the price.

```{r remove_na_price}
# 3. Remove missing house price values
houses_sub <- houses_sub %>%
  filter(!is.na(Price))
```

#### Q4. Make the shadow matrix, and plot Bathroom vs Bedroom2 coloured by missingness on Bedroom2. Why don’t any missing values show up?

```{r shadow_matrix}
# 4. Scatter plot of bath vs. bed coloured by missingess in bed 
houses_sub_shadow <- houses_sub %>%
  bind_shadow()

houses_sub_shadow %>%
  ggplot(aes(x = Bathroom, y = Bedroom2, colour = Bedroom2_NA)) +
  geom_point(alpha = 0.4) +
  # Dark2 palette to accommodate colour blindness
  scale_colour_brewer("Miss bedroom", palette = "Dark2")
```

```{r miss_bath_bed}
# Missingness map with just bathroom and bedroom
houses_sub_shadow %>%
  select(Bathroom, Bedroom2) %>%
  vis_miss()
```

```{r miss_remove_na_bed}
# Missingness map based on missings in bedroom
houses_sub_shadow %>%
  select(Bathroom, Bedroom2) %>%
  filter(is.na(Bedroom2)) %>%
  vis_miss()
```

Missing values don't show because all missing values in bedroom are also missing in bathroom

#### Q5. Impute the missing values for Bedroom2 and Bathroom, by using mean imputation.

```{r impute_mean}
# 5. Impute missing values in bed and bath with their mean
houses_sub_shadow_mean <- houses_sub_shadow %>%
  mutate(Bedroom2 = ifelse(is.na(Bedroom2), mean(Bedroom2, na.rm = TRUE), Bedroom2),
         Bathroom = ifelse(is.na(Bathroom), mean(Bathroom, na.rm = TRUE), Bathroom))

# Mean bed and bath
houses_sub_shadow %>%
  summarise(mean_bed = mean(Bedroom2, na.rm = TRUE),
            mean_bath = mean(Bathroom, na.rm = TRUE))
```


#### Q6. Make a plot of the two variables, with the imputed values coloured. Describe the pattern that you see.

```{r plot_impute_mean}
# 6. Scatter plot of bath vs. bed coloured by imputed values
houses_sub_shadow_mean %>%
  ggplot(aes(x = Bathroom, y = Bedroom2, colour = Bedroom2_NA))  +
  geom_point(alpha = 0.4) +
  scale_colour_brewer("Miss bedroom", palette = "Dark2")
```

#### Q7. Impute the missing values for Bedroom2 and Bathroom, using a linear model on the variable Rooms.

```{r impute_lm}
# 7. Linear regression

# Use houses_sub_shadow and not houses_sub_shadow_mean because houses_sub_shadow_mean
# has already imputed missing values in bath and bed (used the mean)

# Run a linear regression of bedroom on room
br2 <- lm(Bedroom2 ~ Rooms, data = houses_sub_shadow)

# Run a linear regression of bathroom on room
ba <- lm(Bathroom ~ Rooms, data = houses_sub_shadow)
```



#### Q8. Make a plot of the two variables, with the imputed values coloured. Is this better or worse than the mean value imputed values? Explain your thinking.

```{r plot_impute_lm}
# 8. Scatter plot after inputation with linear regression

# Impute missing values for  bedroom and bathroom based on above regression
houses_sub_shadow_linreg <- houses_sub_shadow %>%
  mutate(Bedroom2 = ifelse(is.na(Bedroom2), predict(br2, new = houses_sub_shadow), Bedroom2),
         Bathroom = ifelse(is.na(Bathroom), predict(ba, new = houses_sub_shadow), Bathroom))

# Scatter plot
ggplot(houses_sub_shadow_linreg, 
       aes(x = Bedroom2, y = Bathroom, colour = Bedroom2_NA)) +
  geom_point(alpha = 0.4) + 
  scale_colour_brewer("Miss bedroom", palette = "Dark2")
```




