---
title: "Course 2 Section 2.8 - Your turn"
author: "Jiaying Wu"
date: "05/10/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      fig.width = 6,
                      fig.height = 5,
                      fig.align = "center")
```

### Step 1: Preparing the data

```{r data}
# Load tidyverse
library(tidyverse)

# Load rwalkr
library(rwalkr)

# Read in pedestrian data from 2016 to 2018 for 3 locations
ped_melbcent <- melb_walk_fast(year = 2016:2018, sensor = "Melbourne Central")
invisible(gc())
ped_southbank <- melb_walk_fast(year = 2016:2018, sensor = "Southbank")
ped_bourkest.mallnorth <- melb_walk_fast(year = 2016:2018, sensor = "Bourke Street Mall (North)")

# Row bind 3 data frames
ped_melb.south.bourke <- bind_rows(ped_melbcent, ped_southbank, ped_bourkest.mallnorth)

# Look at the data
glimpse(ped_melb.south.bourke)
```

The variables in the data include:

- Sensor - location of the sensor device

- Date_Time - date and time of the reading

- Date - date (yyyy-mm-dd)

- Time - hour of the day

- Count - total sensor count of pedestrians

```{r}
# Load lubridate
library(lubridate)

# Create 'time' variables
ped_melb.south.bourke <- ped_melb.south.bourke %>%
  mutate(year = year(Date),
         month = month(Date, label = TRUE, abbr = TRUE), 
         wday = wday(Date, label = TRUE, abbr = TRUE, week_start = 1),
         day = day(Date))
```

#### Step 2: Exploring time gaps

Using what you have learned from Visualising Missing data, you will check for missing values/time gaps in the data.

```{r}
library(visdat)
library(naniar)
```

```{r}
#  Melbourne Central time gaps
ped_melb.south.bourke %>% 
  filter(Sensor == "Melbourne Central") %>%
  ggplot(aes(x=Date_Time, y=Count)) + 
  geom_miss_point(size = 0.7) +
  facet_wrap(year ~., scales = "free_x", nrow = 3) +
  labs(title = "Melbourne Central", y = "Count", x = "Date-Time")
```

```{r}
#  Southbank time gaps
ped_melb.south.bourke %>% 
  filter(Sensor == "Southbank") %>%
  ggplot(aes(x=Date_Time, y=Count)) + 
  geom_miss_point(size = 0.7) +
  facet_wrap(year ~., scales = "free_x", nrow = 3) +
  labs(title = "Southbank", y = "Count", x = "Date-Time")
```

```{r}
#  Bourke Street Mall (North) time gaps
ped_melb.south.bourke %>% 
  filter(Sensor == "Bourke Street Mall (North)") %>%
  ggplot(aes(x=Date_Time, y=Count)) + 
  geom_miss_point(size = 0.7) +
  facet_wrap(year ~., scales = "free_x", nrow = 3) +
  labs(title = "Bourke Street Mall (North)", y = "Count", x = "Date-Time")
```

#### Step 3: Visualising the data

return the mean and median hourly pedestrian counts in Melbourne Central, Southbank and Bourke Street Mall (North).

```{r}
# Table of mean and median pedestrian count
ped_melb.south.bourke %>% 
  group_by(Sensor) %>%
  summarise(meanCount = mean(Count, na.rm=TRUE),
            medianCount = median(Count, na.rm=TRUE)) %>%
ungroup()
```

```{r}
# Histogram of pedestrian count
ped_melb.south.bourke %>%
  ggplot(aes(x = Count)) +
  geom_histogram() +
  labs(title = "Distribution of hourly pedestrian count", 
       x = "Pedestrians detected",
       y = "Frequency") +
  facet_wrap(~ Sensor, scales = "free", nrow = 3)
```

#### obtain the median hourly pedestrian counts by location and month.

```{r}
# Median hourly pedestrian count for each month and location
ped_melb.south.bourke %>% 
  group_by(Sensor, month) %>%
  summarise(medianCount = median(Count, na.rm=TRUE)) %>%
  ungroup() %>%
  spread(Sensor, medianCount)
```

```{r fig.width = 6,fig.height = 4}
# Challenge: Line plots median hourly pedestrian count
ped_melb.south.bourke %>% 
  group_by(Sensor, month) %>%
  summarise(medianCount = median(Count, na.rm=TRUE)) %>%
  ungroup() %>%
  ggplot(aes(x= month,  y = medianCount, color = Sensor, group = Sensor)) +
  geom_line() +
  geom_point() +
  labs(title = "Median Hourly Pedestrian Counts, 2016-2018", 
       subtitle = "Generally more pedestrians detected in Southbank across all months.",
       x = "Month", 
       y = "Median Counts")
```

#### Box plots of pedestrian counts

```{r}
# Box plot of pedestrian counts
ped_melb.south.bourke %>% 
  ggplot(aes(x = as.factor(Time), y = Count, colour = Sensor)) + 
  geom_boxplot(alpha = 0.5) +
  facet_wrap(~ year, nrow = 3) +
  theme(legend.position = "bottom") + # change the legend position
  labs(title = "Distribution of pedestrian counts at each hour of the day", y = "Pedestrian Counts", x = "Hour of the day")
```

#### Pedestrian count prior to NYE fireworks

```{r}
# Fill out ??? 
ped_melb.south.bourke %>%
  filter(month == "Dec", day %in% 24:31) %>%
  ggplot(aes(x = Date_Time, y = Count, colour = Sensor)) + 
  geom_line(alpha = 0.5) +
  facet_wrap(year ~., scales = "free_x", nrow = 3) +
  theme(legend.position = "bottom") + # change the legend position
  labs(title = "Pedestrian count at each hour of the day leading up to NYE", y = "Pedestrian Count", x = "Hour of the day")
```


