---
title: "Course 2 Section 2.13 - Your turn"
author: "Jiaying Wu"
date: "13/10/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      fig.width = 6,
                      fig.height = 4,
                      fig.align = "center")
```

```{r}
# Load library
library(tidyverse)
library(nycflights13)
library(ggmap)
```

### Delta flights

```{r}
# La Guardia airport
airports %>% filter(faa == "LGA")
```

### Confirming the point location

Confirm with a Google Map search that the geographical coordinates describing the location of La Guardia airport is in fact a point location in New York City.

#### Q1.Filter the flights data for for Delta Air Line flights from La Guardia in August

```{r}
# Filter Delta flights and create variable of La Guardia's location
delta <- flights %>% 
  filter(carrier == "DL", origin == "LGA", month == 8) %>%
  left_join(airports, by = c("dest" = "faa")) 
```

#### Q2.Create variables orig_lon and orig_lat to add La Guardia airport’s location

```{r}
# Create variables to add the geographical coordinates of LGA's location
delta <- delta %>%
  mutate(orig_lon = filter(airports, faa == "LGA")$lon, 
         orig_lat = filter(airports, faa == "LGA")$lat)
```


#### Q3.Download a map from the Google Maps Platform based on the following geographical coordinates -92.20562 (longitude) and 36.20259 (latitude)

```{r}
# Geographical coordinates of a location of interest
location_US <- c(lon = -92.20562, lat = 36.20259)
```

```{r}
# Enable Google services (need to obtain your Google Map API key first)
register_google(key = "Insert_your_API_key")
```

```{r}
# Download map based on above coordinates (zoom of 4 gives us map of US)
map_US <- get_map(location_US, zoom = 4)
```

#### Q4.Overlay lines connected by the origin and destinations of Delta Air Line flights on this map

```{r}
# Plot map
ggmap(map_US) +
  geom_segment(data = delta,
               aes(x = orig_lon, y = orig_lat, xend = lon, yend = lat),
               color = "navyblue", 
               alpha = 0.2) 
```

### Airport delays

Using the weather and flights data set, perform an analysis to answer the question of whether the wind direction of strong winds affect airport operations.

#### Q5.join the weather data to the flights data

```{r}
library(nycflights13)

flight_weather <- flights %>%
  left_join(weather, by = c("origin", "time_hour"))

flight_weather
```

#### Q6.filter by La Guardia airport and high wind speeds (greater than 25 m/s)

```{r}
flight_weather <- flight_weather %>%
  filter(origin == "LGA", wind_speed > 25)

flight_weather
```

#### Q7.plot departure delay against wind direction, perhaps focusing a restricted range of delay or using only a smoother instead of all the points.

```{r}
ggplot(flight_weather, aes(x = wind_dir, y = dep_delay)) +
  geom_point(alpha = 0.2) +
  geom_smooth(se = FALSE) +
  labs(title = "Departure delay versus Wind direction at La Guardia airport", x = "Wind Direction", y = "Departure Delay (minutes)")
```

