---
title: 'Course 2 Section 3.12 -  BUILDING MANY MODELS: FITTING (PLOT ALL THE MODELS)'
author: "Jiaying Wu"
date: "17/10/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 7,
                      fig.height = 5,
                      fig.align = "center")
```

```{r}
#load library
library(tidyverse)
library(gapminder)
library(broom)
```

```{r}
# Create variable year1952
gapminder2 <- gapminder %>% 
  mutate(year1952 = year-1952)

# Group by country, nest, use mutate to fit a model for each country
by_country <- gapminder2 %>% 
  select(country, year1952, lifeExp, continent) %>%
  group_by(country, continent) %>% 
  nest() %>% 
  mutate(model = purrr::map(data, ~ lm(lifeExp ~ year1952, data = .))) %>%
  ungroup()

# Unnest the model column but do so in a tidy way that returns the intercept and slope coefficient 
country_coefs <- by_country %>% 
  mutate(model = map(model, broom::tidy)) %>%
  unnest(model) %>%
  #Wrangle the data - intercept and slope coefficient as columns
  select(country, continent, term, estimate) %>% 
  spread(term, estimate) %>%
  rename(intercept = `(Intercept)`)

# Extract the R-squared of each country's fitted linear model
country_fit <- by_country %>% 
  mutate(model = map(model, broom::glance)) %>%
  unnest(model)
```

### Give it a go!

filter the top 12 fitted models of life expectancy based on $R^2$ and compare them with the bottom 12 fitted models.

```{r}
# Top and bottom 12 fitted models based on R^2
goodfit <- country_fit %>% 
  top_n(r.squared, n = 12) %>%
  mutate(fit = "goodfit")

badfit <- country_fit %>% 
  top_n(r.squared, n = -12) %>%
  mutate(fit = "badfit") 

# Row bind goodfit with badfit
good_bad_fit <- bind_rows(goodfit, badfit) %>%
  arrange(desc(r.squared))

# Plot to compare R-squared of country's with good and bad fitting models of life expectancy 
good_bad_fit %>%
  ggplot(aes(x = country, y = r.squared)) +
  geom_bar(alpha = 0.5, stat = "identity") +
  facet_wrap(~ fit, nrow = 2, scales = "free_x") +
  labs(title = "Goodness-of-fit of countries with the best and worse fitting model of life expectancy",
       subtitle = "Each country is fitted with a linear model",
       x = "Country", 
       y = "R-squared")
```

compare the estimated slope coefficient of these country’s fitted model of life expectancy.

```{r}
# Join estimated intercept and slope coefficients to good_bad_fit
good_bad_fit <- left_join(good_bad_fit, (country_coefs %>% select(-continent)), by = "country")

# Print the R-squared and estimated slope coefficients
good_bad_fit %>%
  select(country, fit, r.squared, intercept, year1952)
```

```{r}
# Compare the R-squared and estimated slope coefficients for good and bad fitting models
good_bad_fit %>%
  ggplot(aes(x = country, y = year1952)) +
  geom_bar(alpha = 0.5, stat = "identity") +
  facet_wrap(~ fit, nrow = 2, scales = "free_x") +
  labs(title = "Estimated slope coefficients of countries with the best and worse fitting model of life expectancy",
       subtitle = "Each country is fitted with a linear model",
       x = "Country", 
       y = "Estimated slope coefficient")
```

Apply the arrange() function to appropriately arrange columns in country_coefs to answer the following questions. Which country has the:

#### Q1.lowest improvement in life expectancy?

```{r}
country_coefs %>%
  arrange(year1952)
```

#### Q2.highest improvement in life expectancy?

```{r}
country_coefs %>%
  arrange(desc(year1952))
```


#### Q3.lowest initial life expectancy?

```{r}
country_coefs %>%
  arrange(intercept)
```


#### Q4.highest initial life expectancy?

```{r}
country_coefs %>%
  arrange(desc(intercept))
```

