---
title: "Course 2 Section 3.9 - YOUR TURN"
author: "Jiaying Wu"
date: "16/10/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 5,
                      fig.height = 4,
                      fig.align = "center")
```

```{r}
#load library
library(tidyverse)
library(broom)
library(lubridate)
```

```{r}
# Load PISA data file if stored in folder named "data"
load(here::here("data","pisa_au.rda"))
```

### Step 1: Create a variable

Create a variable called science, which represents the student’s science score based on the average of 10 plausible value (PV) scores in science.

```{r}
# Create data frame of science scores
pisa_au_science <- pisa_au %>% 
  # Create science score based on the 10 PV science scores
  mutate(science = (PV1SCIE + PV2SCIE + PV3SCIE + PV4SCIE + PV5SCIE + 
    PV6SCIE + PV7SCIE + PV8SCIE + PV9SCIE + PV10SCIE) / 10)
```

### Step 2: Rename variables

Rename the following variables so that they better reflect what they represent:

- ST094Q01NA represents the student’s enjoyment of science.

- SMINS represents the student’s time spent studying science per week.

- W_FSTUWT represents the student’s weighting, which is an indication of how many other students they represent in Australia, relative to their socioeconomic and demographic characteristics.

- ST004D01T represents the student’s gender (NA is also a category here but there are no NAs for this variable in this data set). Any ‘missingness’ in this variable is information and should not be removed or corrected.

- ANXTEST represents the student’s test anxiety level.

```{r}
pisa_au_science <- pisa_au_science %>% 
  # Select and rename ambiguous names
  select(science, science_fun = ST094Q01NA, science_time = SMINS,
    stuweight = W_FSTUWT, gender=ST004D01T, anxtest = ANXTEST) %>%
  # Recode gender variable
  mutate(gender = factor(gender, 
                            levels=c(1,2),
                            labels=c("girl", "boy")), exclude = NULL)
```

### Step 3: Filter and convert

Filter out anomalies and missing values, and then convert the variables into appropriate classes.

```{r}
pisa_au_science <- pisa_au_science %>% 
  # Filter out missing values in science_time
  filter(!is.na(science_fun), !is.na(science_time)) %>% 
  # Convert science_fun into a factor
  mutate(
    science_fun = as.factor(science_fun),
    science_time = as.numeric(science_time)
  ) %>%
  # Filter for science_time greater than 0
  filter(science_time > 0)
```

### Relationship between science score and time spend studying science

#### Q1.If you did not apply a log transformation to study time, how would you describe its distribution?

```{r fig.width = 6, fig.height = 6}
pisa_au_science %>% 
  ggplot(aes(x = science_time, y = science, colour = science_fun)) + 
  geom_point(alpha = 0.1) + 
  facet_wrap(~ science_fun, ncol = 2) + 
  scale_colour_brewer("Enjoy science", palette = "Dark2") +
  theme(legend.position = "bottom") + 
  ggtitle("Relationship between science score and time spent studying it") +
  labs(subtitle = "Students are grouped based on how much they enjoy science") +
  xlab("Time spent studying science per week*") + 
  ylab("Science score")
```

The study time mostly clumped on the left with a right skewed. 

#### Q2.Based on the log scaled x-axis, how would you describe the relationship between science score and time spent studying?

```{r fig.width = 6, fig.height = 6}
pisa_au_science %>% 
  ggplot(aes(x = science_time, y = science, colour = science_fun)) + 
  geom_point(alpha = 0.1) + 
  facet_wrap(~ science_fun, ncol = 2) + 
  scale_colour_brewer("Enjoy science", palette = "Dark2") +
  # log-scale the x-axis
  scale_x_log10() +
  theme(legend.position = "bottom") + 
  ggtitle("Relationship between science score and time spent studying it") +
  labs(subtitle = "Students are grouped based on how much they enjoy science",
       caption = "*x-axis is plotted on a log scale") +
  xlab("Time spent studying science per week*") + 
  ylab("Science score")
```

More time spent on studying seems to give higher scores. Most of the scores are widely distributed in the middle section, around the median for time spent. 

#### Q3.Are students who enjoy science more likely to receive higher scores, given they spend an equal amount of time studying science?

```{r fig.width = 4, fig.height = 4}
pisa_au_science %>% 
  ggplot(aes(x = science_time, y = science, colour = science_fun)) + 
  geom_point(alpha = 0.1) + 
  #facet_wrap(~ science_fun, ncol = 4) + 
  geom_smooth(method = "lm", se = FALSE) +
  scale_colour_brewer("Enjoy science", palette = "Dark2") +
  # log-scale the x-axis
  scale_x_log10() +
  theme(legend.position = "bottom") + 
  ggtitle("Relationship between science score and time spent studying it") +
  labs(subtitle = "Students are grouped based on how much they enjoy science",
       caption = "*x-axis is plotted on a log scale") +
  xlab("Time spent studying science per week*") + 
  ylab("Science score")
```

Given they spend an equal amount of time studying science, students who enjoy science more likely to receive higher scores.

### Interpret model outputs

fit the 2 models of student’s science scores using the pisa_au_science data. 

Using the output of both fitted models:

```{r}
# Fit both models of student's science score
mod1 <- lm(science ~ log10(science_time) + science_fun,
  data = pisa_au_science, weights = stuweight)
mod2 <- lm(science ~ log10(science_time) * science_fun,
  data = pisa_au_science, weights = stuweight)
```

#### Q4.Provide an interpretation of the intercept coefficients for the first fitted model.

```{r}
tidy(mod1)
```

For model 1, the intercept coefficients implies when the student study science who with a level science enjoyment and spent to 1 minute study science per week, the science score estimated as 267.6791.

#### Q5.Write down each fitted model in equation form.

For model 1, $\hat{science} = 267.6791 + 83.8046*log10(\text{science_time}) + 31.7587*\text{science_fun2} + 63.1158*\text{science_fun3} + 104.3533*\text{science_fun4}$

```{r}
tidy(mod2)
```

For model 2, $\hat{science} = 463.3345 - 0.0040*log_{10}(\text{science_time}) - 151.8829*\text{science_fun2} -166.7660*\text{science_fun3} - 122.4884*\text{science_fun4} \\+ 78.6434*log_{10}(\text{science_time})*\text{science_fun2} + 98.4052*log_{10}(\text{science_time})*\text{science_fun3} \\+ 96.9308*log_{10}(\text{science_time})*\text{science_fun4}$

#### Q6.Which model is better, and why?

```{r}
rbind(glance(mod1), glance(mod2)) %>%
  select(adj.r.squared, AIC, BIC)
```

Since the model 2 have the higher adjust R-squared and lower AIC, model 2 is preferred.

Note: When you looking at the BIC, model 1 have the lower BIC. And model 1 might have more interpretability than model 2. You can also choose model 1 base on the BIC and interpretability, it's a judgement between interpretability and accuracy.

### Give it a go!

It’s now your turn to fit two models of science score using information about the student’s gender and anxiety level:

#### Q7.A model of science score against gender and test anxiety level.

```{r}
# Fit the models
sci_lm1 <- lm(science ~ gender + anxtest, data = pisa_au_science, weights = stuweight)

# Output of first fitted model
tidy(sci_lm1)
```

```{r}
glance(sci_lm1)
```


#### Q8. A model of science score with an interaction between gender and test anxiety level.

```{r}
sci_lm2 <- lm(science ~ gender * anxtest, data = pisa_au_science, weights = stuweight)

# Output of second fitted model
tidy(sci_lm2)
```

```{r}
glance(sci_lm2)
````









