---
title: "Course 2 Section 3.6 - OPTIMISATION"
author: "Jiaying Wu"
date: "16/10/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      fig.width = 5,
                      fig.height = 4,
                      fig.align = "center")
```

```{r}
#load library
library(tidyverse)
library(broom)
```

### Give it a go

Continue to develop your understanding of the OLS estimator, optimal fitted line and residuals by making your way through this exercise. You’ll need to use a pen or pencil and paper to produce your work, which you can then share with other learners.

Below is a data set with 5 observations for the two variables, x and y:

```{r}
df <- tibble(x=c(1.5, 2, 3.1, 3.9, 5), y=c(3.7, 4.6, 5.5, 5.7, 7.2))
df
```

Training a linear model of y using this data set produces the following equation:

```{r}
fit_model <- lm(y ~ x, df)
tidy(fit_model)
```

$\hat{y} =  2.5338 + 0.9052x$

#### Q1.compute the fitted values of y, i.e., the prediction of y for each value of x.

```{r}
df <- df %>%
  mutate(y_hat = predict(fit_model))

df
```

#### Q2.use the predictions to compute the residuals and then the SSR

```{r}
df <- df %>%
  mutate(residual = residuals(fit_model))

df
```

```{r}
# SSR
sum(df$residual ^ 2)
```


### Repeat the exercise above using the following less optimal fitted model:

$\hat{y} =  2.5 + 1.1x$

#### Q3.compute the fitted values of y

```{r}
df2 <- tibble(x=c(1.5, 2, 3.1, 3.9, 5), y=c(3.7, 4.6, 5.5, 5.7, 7.2)) %>%
  mutate(y_hat = 2.5+1.1*x)

df2
```

#### Q4.use the predictions to compute the residuals and then the SSR

```{r}
df2 <- df2 %>%
  mutate(residual = y - y_hat)

df2
```

```{r}
# SSR
sum(df2$residual ^ 2)
```

