---
title: "Course 3 Step 1.10 - TURNING TEXT INTO DATA"
author: "Jiaying Wu"
date: "18/10/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 5,
                      fig.height = 4,
                      fig.align = "center")
```

```{r}
# Load library
library(tidyverse)
library(gutenbergr)
library(tm)
library(tidytext)
library(plotly)

# Download the 1st edition of On the Origin of Species (ID 1228)
darwin1 <- gutenberg_download(1228)

# Remove numbers from text
darwin1$text <- removeNumbers(darwin1$text)

# Tokenise text 
darwin1_words <- darwin1 %>% 
  unnest_tokens(word, text)

# Remove stop words then count and arrange words
darwin1_words <- anti_join(darwin1_words, stop_words, by = "word") %>%
  count(word, sort = TRUE) %>%
  mutate(len = str_length(word)) # Create a variable of the no. of characters in each word 

# Download the 6th edition (ID 2009)
darwin6 <- gutenberg_download(2009)

# Remove numbers from text
darwin6$text <- removeNumbers(darwin6$text)

# Remove stop words then count and arrange words
darwin6_words <- darwin6 %>% 
  unnest_tokens(word, text) %>%
  anti_join(stop_words, by = "word") %>%
  count(word, sort = TRUE) %>%
  mutate(len = str_length(word)) 

# Create variable of book edition
darwin1_words <- darwin1_words %>%
  mutate(edition = "1")

darwin6_words <- darwin6_words %>%
  mutate(edition = "6")

# Row bind both books
darwin <- bind_rows(darwin1_words, darwin6_words)
```

### Give it a go!

Generate an interactive scatter plot of the word frequency from the 6th and 1st edition of Charles Darwin’s book of evolutionary theory.

```{r}
# Word count from both editions 
darwin <- full_join(darwin1_words, darwin6_words, by = "word") %>%
  rename(n_ed1 = n.x, len_ed1 = len.x, n_ed6 = n.y, len_ed6 = len.y)

# Scatter plot of word count frequency from the 6th and 1st edition
p <- ggplot(darwin, aes(x=n_ed1, y=n_ed6, label=word)) + 
  geom_abline(intercept=0, slope = 1) +
  geom_point(alpha=0.5) +
  xlab("1st edition") + ylab("6th edition") +
  scale_x_log10() + scale_y_log10() + theme(aspect.ratio=1)

# Interactive scatter plot plot
ggplotly(p)
```

#### Q1.Does it look like the 6th edition was an expanded version of the first?

Yes, the most of the words appear more frequently in the 6th edition.

#### Q2.What word is most frequent in both editions?

species.

#### Q3.Which words are not in the first edition but appear in the 6th?

```{r}
darwin %>%
  filter(is.na(n_ed1))
```

2209 words are not in the first edition but appear in the 6th, including "mivart", "prof", "cambrian"...

#### Q4.Which words that are used the first edition but not in the 6th?

```{r}
darwin %>%
  filter(is.na(n_ed6))
```

269 words are used the first edition but not in the 6th, including "deg", "experimentised", "weald"...


