---
title: "Course 3 Step 1.11 - SENTIMENT ANALYSIS"
author: "Jiaying Wu"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 8,
                      fig.height = 5,
                      fig.align = "center")
```

```{r}
# text analysis
library(tidyverse)
library(tidytext)

# text data
library(janeaustenr)

# grid arrange
library(gridExtra)
library(grid)

# date
library(lubridate)
```

### Give it a go!

### Jane Austen

You have seen how a lexicon can be used to compute the proportion of positive and negative words in Jane Austen’s ‘Emma’.

Using your choice of a lexicon (NRC, Bing, or AFINN), in RStudio compute the proportion of positive and negative words in each of Jane Austen’s books.

```{r}
# Tokenise text in Emma
Emma <- austen_books() %>%
  filter(book == "Emma") %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]", 
                                                 ignore_case = TRUE)))) %>%
  unnest_tokens(word, text)
```

```{r}
# Get bing lexicon
bing <- get_sentiments("bing")

# Inner join bing to the tidied text of Emma
Emma_sen <- Emma %>%
  inner_join(bing)
```

```{r}
# Most common positive words
p_positive <- Emma_sen %>%
  filter(sentiment == "positive") %>%
  count(word, sort = TRUE) %>%
  top_n(10, n) %>%
  ggplot(aes(x = fct_reorder(word, n), y = n)) + 
  geom_col(fill = "lightgreen") +
  labs(x = "", title = "Most common positive words", caption = "") +
  coord_flip() +
  theme(axis.title.x = element_blank())  

# Most common negative words
p_negative <- Emma_sen %>%
  filter(sentiment == "negative") %>%
  count(word, sort = TRUE) %>%
  top_n(10, n) %>%
  ggplot(aes(x = fct_reorder(word, n), y = n)) + 
  geom_col(fill = "red") +
  labs(x = "", title = "Most common negative words", caption = "Word sentiment based on Bing Lexicon") +
  coord_flip() +
  theme(axis.title.x = element_blank())  

grid.arrange(p_positive, p_negative, 
             nrow = 1, 
             top = textGrob("Words that appear most frequently in Jane Austen's book Emma"),
             bottom = textGrob("Frequency"))
```


### AFL

Notice that the Melbourne Football Club, whose Twitter handle is melbournefc, was the 10th most frequent tweeter using the #AFLFinal hashtag and the only football club on this list.

Using the sentiment analysis above, try to answer the following questions:

#### Q1.Which tweeter is the most positive and the most negative?

```{r}
# Read the afl data from GitHub
afl <- read_csv("https://raw.githubusercontent.com/datascienceprogram/ids_course_data/master/afl.csv")

# Tokenise each tweet, join the AFINN lexicon, calculate the average sentiment score by status ID (tweet)
afl_sentiment <- afl %>% 
  group_by(status_id) %>% # status ID is a tweet ID
  unnest_tokens(word, text) %>%
  inner_join(get_sentiments("afinn")) %>%
  summarise(sentiment = mean(value, na.rm = T)) %>% # sentiment score of each word in a tweet is averaged
  ungroup()

# Join tweet data to afl_sentiment - gives us sentiment score 
afl_sentiment <- afl %>% 
  select(status_id, screen_name, created_at, text) %>% 
  left_join(afl_sentiment, by = "status_id")
```

##### The most positive tweets

```{r}
afl_sentiment %>%
  filter(sentiment == max(sentiment, na.rm = TRUE))
```

##### The most negative tweets

```{r}
afl_sentiment %>%
  filter(sentiment == min(sentiment, na.rm = TRUE))
```


#### Q2.Is there a day that spirits were higher in the tweets or when tweets were more negative?

```{r}
afl %>%
  mutate(Day = day(created_at)) %>%
  count(Day, sort = TRUE) %>%
  ggplot(aes(x = as.factor(Day), y = n)) +
  geom_col(alpha = 0.8, fill = "lightgreen") +
  labs(x = "Day",
       y = "Frequency",
       title = "Total tweets containing #AFLFinal by day - Sep 3rd to 13th, 2019")
```

Day 8 is higher in the tweets.

```{r}
afl_sentiment %>% 
  mutate(day = ymd(as.Date(created_at))) %>% 
  group_by(day) %>%
  summarise(mean_sentiment = mean(sentiment, na.rm = TRUE)) %>%
  ungroup() %>%
  ggplot(aes(x = day, y = mean_sentiment)) + 
  geom_col(alpha = 0.8 , fill = "lightblue") + 
  scale_x_date(date_labels = "%a %d", date_breaks = "1 day") +
  labs(x = "Date",
       y = "Average sentiment score",
       title = "Sentiment score of all tweets containing #AFLFinals -  Sep 3rd to 13th, 2019",
       caption = "Words tagged with a sentiment scored between -5 to 5 from the AFINN lexicon")
```

The tweets in September 3rd were more negative than other days.


#### Q3.Does the tweeter aflratings have a trend in positivity or negativity?

```{r}
# Sentiment score from all tweets containing #AFLFinal between Sep 3rd to 13th by @aflratings
afl_sentiment %>% 
  filter(screen_name == "aflratings") %>% 
  mutate(day = ymd(as.Date(created_at))) %>%
  ggplot(aes(x=day, y=sentiment)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  scale_y_continuous(limits = c(-5,5), breaks = seq(-5,5,1)) +
  scale_x_date(date_labels = "%a %d", date_breaks = "1 day") +
  labs(
    x = "Date",
    y = "Average sentiment score",
    title = "Sentiment score of all tweets containing #AFLFinals by @aflratings -  Sep 3rd to 13th, 2019",
    caption = "Words tagged with a sentiment scored between -5 to 5 from the AFINN lexicon")

```

The tweeter aflratings have a trend in negativity.
