---
title: "Course 3 Step 1.15 - Network data"
author: "Jiaying Wu"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 8,
                      fig.height = 6,
                      fig.align = "center")
```

### Mad Man

#### Using geomnet to work with network data

```{r}
# library
library(tidyverse)
library(geomnet)

# Load madmen (list of 2 data frames)
data(madmen)
```

#### Apply some data pre-processing

Use the fortify() function to join the vertices and edges data (madmen$vertices and madmen$edges).

```{r}
# Data step: Join the edge and node data with a fortify call
MMnet <- fortify(as.edgedf(madmen$edges), madmen$vertices)
```

#### Positioning associated vertices

```{r}
# Create network diagram
set.seed(5556677) # seed set to ensure that network diagram does not change on each run

ggplot(data = MMnet, aes(from_id = from_id, to_id = to_id)) +
  geom_net(aes(colour = Gender), layout.alg = "kamadakawai", # Layout algorithm
           size = 2, labelon = TRUE, vjust = -0.6, ecolour = "grey60",
           directed = FALSE, fontsize = 3, ealpha = 0.5) +
  scale_colour_manual(values = c("#FF69B4", "#0099ff")) +
  xlim(c(-0.05, 1.05)) +
  theme_net() +
  theme(legend.position = "bottom")
```

### American college football

```{r}
# Load football (list of 2 data frames)
data(football)
```

#### Join the vertices and edges data frame, and create a variable

```{r}
# Join the edge and node data with a fortify call
ftnet <- fortify(as.edgedf(football$edges), football$vertices)

# Label independent schools
ftnet$schools <- ifelse(ftnet$value == "Independents", ftnet$from, "")

# Create network diagram
set.seed(1)
ggplot(data = ftnet, aes(from_id = from_id, to_id = to_id)) +
  geom_net(aes(colour = value,
               group = value,
               linetype = factor(1-same.conf),
               label = schools),
           linewidth = 0.5,
           size = 4,
           fontsize = 3,
           vjust = -0.75, 
           alpha = 0.5,
           layout.alg = 'fruchtermanreingold') +
  scale_linetype_discrete(name = "Same Conference", labels = c("Yes", "No", "NA")) +
  theme_net() +
  theme(legend.position = "bottom", legend.box = "vertical") +
  guides(colour = guide_legend(order = 1),
         linetype= guide_legend(order = 2)) +
  scale_colour_brewer("Conference", palette = "Paired")
```

### Give it a go!

Further develop your skills and knowledge of working with data by creating network diagrams based on characters in Harry Potter.

In the network diagram, the Harry Potter characters will be the vertices and the edges occur if one character provides emotional support to the other at some point in the book.

#### Load the data

```{r}
# URL of raw text of HP characters
hp.chars_URL <- "https://raw.githubusercontent.com/datascienceprogram/ids_course_data/master/hp.chars.csv"

# Read HP characters data
hp.chars <- read_csv(hp.chars_URL)

# URL of raw text of HP edges
hp.edges_URL <- "https://raw.githubusercontent.com/datascienceprogram/ids_course_data/master/hp.edges.csv"

# Read HP edges data
hp.edges <- read_csv(hp.edges_URL)

# Convert to data frame object
hp.chars <- as.data.frame(hp.chars)
hp.edges <- as.data.frame(hp.edges)
```

#### Determine the edges and vertices

Create a facetted network diagram of the Harry Potter characters.

```{r fig.width = 9,fig.height = 7}
# Join the edge and node data with a fortify call
hp.all <- fortify(as.edgedf(hp.edges), hp.chars, group = "book") # group by HP book for facetting

# Create network diagram facetted by book
set.seed(12345)
ggplot(data = hp.all, aes(from_id = from, to_id = to_id)) + 
  geom_net(fiteach=T, directed = T, size = 2, linewidth = .5, 
           ealpha = .5, labelon = T, fontsize = 2, repel = T, 
           labelcolour = "black", arrowsize = .5, singletons = FALSE,
           aes(colour = house, group = house, shape = gender)) + 
  scale_colour_manual(values = c("#941B08","#F1F31C", 
                                 "#071A80", "#154C07")) + 
  facet_wrap(~book, labeller = "label_both", ncol = 3) + 
  theme_net() + 
  theme(panel.background = element_rect(colour = 'black'), legend.position = "bottom")
```


